Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-16 paper/main.tex
remove sentence for diffusion
remove supplement subsection and link to it

\textbf{TODO what is the parameter $s$? Explain more clearly.}\\
To remove this non-identifiability we reduce the number of parameters by setting $\gamma=\gamma_0/s$
and $\eta=\eta_0 s$ for the rod rigidity and spring tension, resp.
We then optimize for this parameter and pick $\gamma_0=\SI{15}{\micro\metre}$ with
$\eta_0=\SI{150}{\micro\metre\per\second\squared}$ which corresponds to $60\%$ of the previously considered
interval.
The corresponding plots can be seen in \ref{subsec:supplement-parameter-profiles-amir}.
\textbf{TODO Make this more clear. Transient information would lead to more information. We only
have initial and final snapshots.}

@@

% For this dataset, we assumed that all parameters which specify the interaction potential are
% identical across all agents but growth rates of the cells are individual.
We chose to optimize for the damping of agents' movement within the medium, 3 interaction parameters
of the Mie potential $n,m,V_0$ a single radius $r$ for all agents and growth rates which were chosen
individually for each cell.
We removed any stochastic motion contributions by setting $D=0$.
This leads to a total of $5+1\times 6=11$ variable parameters.
As highlighted before, in order to model non-flexible rods, we set the rigidity and spring tension
of the rod to a high, fixed value.
To estimate these parameters we used the differential evolution~\cite{Storn1997} global optimization
algorithm which was initially seeded with a sample generated by the latin-hypercube~\cite{McKay1979}
method.
Finally, we performed a local minimization using the L-BFGS-B algorithm~\cite{Liu1989}.

@@

\subsubsection{Amir}
\label{subsec:supplement-parameter-profiles-amir}

The parameter ranges were chosen such that a suitable 
Plots are chosen for visual ease; parameter ranges have been widened to ensure results are
accurate (maybe just leave this in the appendix).

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/fit-comparison.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/drag force.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/growth rate.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/rod rigidity.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/rigidity to spring tension ratio.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/damping.pdf}%
        \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO}
    }
\end{figure}

>>>>

\textbf{TODO what is the parameter $s$? Explain more clearly.}\\
To remove this non-identifiability we reduce the number of parameters by setting $\gamma=\gamma_0/s$
and $\eta=\eta_0 s$ for the rod rigidity and spring tension, resp.
We then optimize for this parameter and pick $\gamma_0=\SI{15}{\micro\metre}$ with
$\eta_0=\SI{150}{\micro\metre\per\second\squared}$ which corresponds to $60\%$ of the previously considered
interval.
\textbf{Plots are not in supplement anymore}
The corresponding plots can be seen in \textbf{TODO}.
\textbf{TODO Make this more clear. Transient information would lead to more information. We only
have initial and final snapshots.}

@@

% For this dataset, we assumed that all parameters which specify the interaction potential are
% identical across all agents but growth rates of the cells are individual.
We chose to optimize for the damping of agents' movement within the medium, 3 interaction parameters
of the Mie potential $n,m,V_0$ a single radius $r$ for all agents and growth rates which were chosen
individually for each cell.
This leads to a total of $5+1\times 6=11$ variable parameters.
As highlighted before, in order to model non-flexible rods, we set the rigidity and spring tension
of the rod to a high, fixed value.
To estimate these parameters we used the differential evolution~\cite{Storn1997} global optimization
algorithm which was initially seeded with a sample generated by the latin-hypercube~\cite{McKay1979}
method.
Finally, we performed a local minimization using the L-BFGS-B algorithm~\cite{Liu1989}.

@@
